FAIR fission track analysis with geochron@home

### 2025-07-21 geochron@home/manuscript/paper.tex
Finished Figure 3

%\begin{figure}[!ht]
{ \centering \includegraphics[width=\linewidth]{radialcrowd.pdf}
  \captionof{figure}{a) box plots of 25 crowd-sourced sets of fission
    track counts for 69 analysts; b) comparison of grains~23 and 25,
    which were chosen because of their high counts and variability; c)
    radial plot of the pairwise ratios of the fission track counts for
    grains~23 and 25. The results of analyst PV are shown in
    blue.\medskip}
  \label{fig:radialcrowd}
}%\end{figure}

>>>>

%\begin{figure}[!ht]
{ \centering \includegraphics[width=15cm]{radialcrowd.pdf}
  \captionof{figure}{a) Box plots and summary statistics of numbers of
    spontaneous fission tracks counted in each of 25 grains by 68
    novice counters (geology students) all using the same ROIs. Each
    student counted tracks in a subset of the grains. b) The track
    counts for Grain 23 plotted against those for Grain 25 for 37
    students who counted both of those grains. c) Radial plot of the
    ratios of the counts in panel b) using the precisions given by
    Equation~\ref{eq:N12}. In each panel, the counts made by PV are
    added as blue dots.\medskip}
  \label{fig:radialcrowd}
}%\end{figure}
